---
title: "Comparable data format"
author: "Alexander Matrunich"
date: "12/05/2014"
output: html_document
---

# Comparison of trading values

## Initial point

Finally we want to compare measured variables (USD, net weight, etc.) where all identity variables (units, countrycodes) are brought to a common standard.

While we are not sure that all conversion details are taken into account, it's better to have information about all id variables from both parties at hand.

Data downloaded from FAOSTAT3 has following structure:
```{r faostat3_format, echo=FALSE}
library(fclhs)
mxcfao3 <- read.table(system.file("extdata", 
                                  "mxc_2011_2007_all_all.csv.gz", 
                                  package = "fclhs"), 
                      header = T,
                      sep = ',', stringsAsFactors = F,
                      nrows = 63582 # drop final line with timestamp
                      )
str(mxcfao3, vec.len = 1)
```

Data gathered with UN Comtrade API is:

```{r comtrade_format, echo=FALSE}
mxcus <- getunct(area = unctarea(138),
                 year = 2011,
                 partner = 842, #USA
                 desc = T,
                 compact = F)
str(mxcus, vec.len = 1)
```

Id variables we need to take into account:

* Country
* Measurement units
* Flow / elements
* Items / commodities
* Flags (for analysis)
* Year

Currently we compare mutually exclusive groups of interconnected items from FCL and HS2007 sets. For manual checkings we need a way of instant getting of information about items included in group and description of them.

Checks about compatibility have to be done before merging into groups.